---
title: "Demo of rstrap mode in R Markdown"
---

# About this website

This website is a showcase on how it would look like using **rstrap mode**

# What is rstrap ? 

`rstrap` is a forked of Bootstrap specially built to be used with **rmarkdown** with minimal default features, and redistributed under a new distribution name.

Obviously, using `rstrap` will not enable all features of R Markdown but it can be useful for some users to have this special distribution.

In most case this is not to be used. You would need this only when

* You can't use Bootstrap own distribution for any reason, 
* You need more from just deactivating Bootstrap usage in **rmarkdown** by setting `theme = NULL` or `template = NULL` is [`html_document()`](https://rmarkdown.rstudio.com/docs/reference/html_document.html)
* You would then be able to use a fork of Bootstrap maintained and provided by RStudio PBC.

If you wandered the web and came across this page instead of being pointed to it, then it means you probably don't need this. 

## How rstrap is built ?

[Bootstrap](https://github.com/twbs/bootstrap) is MIT licence. This allows us to build our own fork. From Bootstrap sources, we build a special CSS and JS that we rename `rstrap` and that we provide as HTML dependency in **rmarkdown** R package.

Currently, `rstrap` is built from Bootstrap 4. Current prototype work: 

* Special format `rstrap_document()`: https://github.com/rstudio/rsformat
* Integration in rmarkdown: https://github.com/rstudio/rmarkdown/tree/rstrap

## How to use rstrap ? 

`rstrap` will be used when **rmarkdown** opt-in what we called _rstrap\_mode_. This will happen on two conditions: 

```{r, echo = FALSE, include = FALSE}
rmd_fold <- glue::glue("`<lib-path>/rmarkdown/{folder}`",
           folder = 
             fs::path_rel(
               fs::path_package("rmd", "h", "bootstrap", package = "rmarkdown"),
               fs::path_package(package = "rmarkdown")
             )
)
```

* `bootstrap` dependency folder inside **rmarkdown** package installed on a system is not present - we mean this folder `r rmd_fold`

* `rmarkdown.rstrap` is set to `TRUE` - this is useful for tests and demo (like this website)


# Limitations

## Theming is deactivated

All theming behavior from R Markdown will be deactivated. Theming mainly use Bootswatch themes which are not including into `rstrap`. 

This means than `theme` argument in `html_document()` has been deactivated. A warning will be thrown once by R session: 

```{r rstrap-theme-warning, echo = FALSE}
tmp <- tempfile()
dummy <- callr::r(function() rmarkdown:::resolve_theme("cerulean"), stderr = tmp)
xfun::file_string(tmp)
unlink(tmp)
```


## Other R Markdown format

_rstrap\_mode_ is aimed to be used with `html_document()` only. This can't be used with other output formats. 
