---
title: "Example using `r params$title`"
output: 
  html_document:
    code_download: true
    code_folding: hide
    toc: true
    toc_float: true
    anchor_sections: TRUE
params:
  title: rstrap
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rstrap_mode <- function() identical(params$title, "rstrap")
```

# About R Markdown and Bootstrap

R Markdown document uses Bootstrap by default to enable some features (tabs, navbar, ...) and allow easy theming. These requires Bootstrap because they use some of its default component i.e Buttons, Dropdown, Navbar, Navs, ...

In this document, we add basic component (text, table, plot) and we use the Bootstrap dependents features to show how it will render when rstrap mode is activated.

```{css, echo = FALSE, eval = isFALSE(rstrap_mode())}
div.alert > p:last-child {
    margin-bottom: 0;
}

div.alert + p {
  text-align: right;
}
```


```{asis, bootstrap_alert, echo = isFALSE(rstrap_mode())}
::: {.alert .alert-success role="alert"}
[]{.glyphicon .glyphicon-info-sign} This documents is using Bootstrap dependency and not rstrap. This is why the default theming is a bit difference. See Browser inspector to check for dependencies in HTML's `<head>`
:::

<small>[]{.glyphicon .glyphicon-arrow-up} and that is why this alert box and icons are showing.</small>
```

YAML header is this document is 

```yaml
output: 
  html_document:
    code_download: true
    code_folding: hide
    toc: true
    toc_float: true
```

No need to change the output format field to opt-in to rstrap - it is done automatically depending on opt-in condition. See [Home page](index.html)

## Navbar

This website is built with R Markdown website generator and the navbar is the one used with rstrap mode. 

## Code Folding

This document uses `code_folding: hide` in YAML header. 

## Table of content

This document uses

```yaml
toc: true
toc_float: true
```

to add a TOC in the document

## Code download button

This document source code is embedded in the HTML page and available using the Code Download button. `code_download: true` has been set in YAML header.

# Including a table

## Using GT {#gt}

This is a table using gt package

```{r gt-head, fig.cap="Table 1: penguins data using gt"}
library(palmerpenguins)
library(gt)

penguins %>% 
  head(10) %>%
  gt() %>%
  tab_header(md("Head (10 rows) of _penguins_ dataset from **palmerpenguins**")) %>%
  tab_source_note(md("datasource: **palmerpinguins** R package."))
```

<br>

## Using DT {#dt-table}

Another type of table is interactive HTML table like those with the package **DT**

```{r dt-table, echo = TRUE}
DT::datatable(head(penguins, 50), class = 'cell-border stripe',
              caption = 'Table 2: Penguins data using DT')
```

By default, in recent version of **DT**, `style = "auto"` - this means that DT will use Bootstrap styling by default only if **bslib** package is in use (Shiny Apps or Rmd document using **bslib**). Otherwise, it will use default [DataTable styling](https://datatables.net/manual/styling/classes). By setting `style = "default"`, this insure not Bootstrap related styling. 

> **DT** does not come with Bootstrap, it assumes that it is available already on the page when `style = "bootstrap"` is used.

This means that the table above will be different depending on which document you are viewing, the one with Bootstrap or the one with rstrap.

## Including Plots

You can also embed plots, for example:

```{r mass_flipper, fig.alt = "Penguin mass vs. flipper length", message=FALSE, warning=FALSE}
library(ggplot2)
mass_flipper <- ggplot(data = penguins,
                       aes(x = flipper_length_mm,
                           y = body_mass_g)) +
  geom_point(aes(color = species,
                 shape = species),
             size = 3,
             alpha = 0.8) +
  theme_minimal() +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(title = "Penguin size, Palmer Station LTER",
       subtitle = "Flipper length and body mass for Adelie, Chinstrap and Gentoo Penguins",
       x = "Flipper length (mm)",
       y = "Body mass (g)",
       color = "Penguin species",
       shape = "Penguin species") +
  theme(legend.position = c(0.2, 0.7),
        legend.background = element_rect(fill = "white", color = NA),
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position = "plot")

mass_flipper
```

## Examples with tabs {.tabset}

### Plot

```{r mass_flipper, opts.label = TRUE, echo = FALSE}
```

### Table

```{r gt-head, echo = FALSE}
```


## Other features 

### Math

Math does not depend on Bootstrap and still works.

$$
z = x/y + \alpha
$$

## Some rstrap feature still available from Bootstrap

With default rmarkdown document, Bootstrap special components can be defined directly as HTML. This is not available with rstrap mode in a lightweight version

### Example with Alert

This will `r if(rstrap_mode()) "not"` work as the Alert JS and CSS component are `r if(rstrap_mode()) "not"` including in `r if(rstrap_mode()) "rstrap" else "Bootstrap"`.

```{r, echo = FALSE}
htmltools::div(class = "alert alert-primary", role = "alert", 
               "This is a primarty alert box and should be highlighted as such")
```

